Usage metrics

### 2020-12-21 analysis/usage.Rmd
minor

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
  calls_path: package/summarized.fst
  corpus_path: corpus.fst
  static_path: package-evals-static.csv
  force_rebuild: FALSE
---

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
  calls_path: base/summarized.fst
  corpus_path: corpus.fst
  static_path: package-evals-static.csv
  force_rebuild: TRUE
---
